A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-16 main.tex
とりあえずpush

It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, strong normalization, and progress.

The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses in a dependent type system.
CSP is a function of a multi-stage calculus which allows using a value in quoted code.

@@

\blue{203 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
%
%
%
\section{Introduction}
\subsection{Multi-Stage Calculus}
\subsubsection{Introduction to Multi-Stage Calculus}
\subsubsection{Application to Performance Imporving}
\subsection{Dependent Types}
\subsubsection{Introduction to Dependent Types}
\subsubsection{Application to Omitting Boundary Checking}
\subsection{Organaization of the Paper}

\section{Informal Overview of \LMD}
\subsection{\LLF}
\subsection{\LTP}

@@

\subsection{Type System}
\subsubsection{Kinding Rules}
\subsubsection{Equivalence Rules}

\subsection{Properties}

@@

>>>>

It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
It also includes an evaluation context which satisfies unique decomposition.

The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.

@@

\blue{213 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
%
%
%
\section{Introduction}
\subsection{Multi-Stage Calculus}
\subsubsection{Introduction to Multi-Stage Calculus}
\subsubsection{Application to Performance Imporving}
\subsection{Dependent Types}
\subsubsection{Introduction to Dependent Types}
\subsubsection{Application to Omitting Boundary Checking}
\subsection{Organaization of the Paper}

\section{Informal Overview of \LMD}
\subsection{\LLF}
\subsection{\LTP}
\subsection{\LMD}

@@

\subsection{Type System}
\subsubsection{Equivalence Rules}

\begin{definition}[Staged Reduction]
$A \neq \epsilon$\\
\begin{align*}
    E^A_\epsilon [(\lambda x:\tau.M)\ v^\epsilon] & \longrightarrow_s E^A_\epsilon[M[x\mapsto v^\epsilon]] \\
    E^A_\epsilon [(\Lambda\alpha.v^\epsilon)\ \epsilon] & \longrightarrow_s E^A_\epsilon[v^\epsilon[\alpha\mapsto \epsilon]] \\
    E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha] & \longrightarrow_s E^A_\alpha[v^\alpha] \\
\end{align*}
\end{definition}

\begin{definition}[Evaluation Context]
$A \neq \epsilon$\\
\begin{align*}
    E^\epsilon_B \in ECtx^\epsilon_B & ::= \square\ (\text{if\ } B = \epsilon) \mid E^\epsilon_B\ M \mid v^e\ E^\epsilon_B
                                           \mid \TB_\alpha E^\alpha_B \mid \Lambda\alpha.E^\epsilon_B
                                           \mid E^\epsilon_B\ \epsilon  \\
    E^A_B \in ECtx^A_B & ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B
                                           \mid E^\epsilon_B \mid \TB_\alpha E^{A\alpha}_B
                                           \mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A) \\
                                           & \quad \mid \Lambda\alpha.E^\epsilon_B
                                           \mid E^A_B\ \epsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)\\
\end{align*}
\end{definition}

\section{Properties of \LMD}

@@

\begin{theorem}[Unique Decomposition]
    If $x:\tau@\epsilon \notin \G$ and $\G \V M : \tau @ A$ then 1 or 2 is true.
    \begin{enumerate}
        \item $ M \in V^A$
        \item $\exists ! B, E^A_B, R^B$ such that ($B = \epsilon$ or $B = \beta$) and $M = E^A_B[R^B]$.
    \end{enumerate}
\end{theorem}
